CUDA-accelerated genetic feedforward-ANN training for data mining

### 2010-07-10 doc/HPCS-proceedings-paper.tex
Specify the number of passes and adjust the percentiles
git-svn-id: http://svn.scesoc.ca/evolution/trunk@128 fee98b4c-d1c3-4d34-9525-a468159e4a48

Because fast on-chip memory (16~KB) is not large enough for our value of $k$ ($4 * 18936 =$ 74~KB), we instead use $p$ passes of $\frac{k}{p}$-sized heaps. Each pass examines only values which are less than the threshold calculated by the preceeding pass. For example, the third pass examines only values below the 10\% threshold and finds the top 5\% threshold of this subset of values. This threshold therefore is the 15\% threshold of the full list. The threshold calculated by the last pass is the desired 20\% threshold.

>>>>

Because fast on-chip memory (16~KB) is not large enough for our value of $k$ ($4 * 18936 =$ 74~KB), we instead use $p$ (5) passes of $\frac{k}{p}$-sized heaps. Each pass examines only values which are less than the threshold calculated by the preceeding pass. For example, the third pass examines only values below the 8\% threshold and finds the top 4\% threshold of this subset of values. This threshold therefore is the 12\% threshold of the full list. The threshold calculated by the last pass is the desired 20\% threshold.
